\large Neural and Symbolic Optimization of Cosmological Particle-Mesh Simulation \vspace{0.3em}

### 2023-09-25 docs/papers/sto/so.tex
FIXUP draft minor

\subsection{Feature Importance}
We use the random forest regressor for feature selection using impurity-based
importance.
\YZ{Maybe we can add another column in \autoref{tab:feat} for feature
importance?}

\subsection{Symbolic Expressions}
We use the \texttt{scikit-learn} \citep{scikit-learn} code for this.
% more details on the hyperparams in random forest

@@

We generate a sample of (input, output) data with the trained neural network to
perform feature importance analysis.

>>>>

\subsection{Feature Importance}

We generate a sample of (input, output) data of the trained neural network to
perform feature importance analysis.
We use Sobol sequence to generate the sample of (parameters in
\autoref{tab:param}, $k$, $a$).

We use the random forest regressor for feature selection using impurity-based
importance.
We use the \texttt{scikit-learn} \citep{scikit-learn} code for this.
% more details on the hyperparams in random forest
\YZ{Maybe we can add another column in \autoref{tab:feat} for feature
importance?}

\subsection{Symbolic Expressions}

@@
